A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-15 manuscript/manuscript.tex
made minor clarification changes suggested by reviewer

While basic Study classes are typically associated with single image
modality or contrast, the analysis suites implemented by them can be
integrated into multi-modal analysis by aggregating multiple Study
classes (sub-studies) in a \emph{MultiStudy} class. Analysis suites are
integrated by joining the data specification tables of the sub-studies
of a MultiStudy class. Entries in specification tables of sub-studies
are joined by mapping them to a common entry in the specification table
of the MultiStudy (Figure \ref{fig:example_multi_study}). This enables derivatives from one
sub-study (e.g. brain extracted T1-weighted anatomical) to be referenced
by workflows of other sub-studies (e.g. anatomically constrained DWI
tractography).

>>>>

While basic Study classes are typically associated with single image
modality or contrast, the analysis suites implemented by them can be
integrated into multi-modal analysis by aggregating multiple Study
classes (sub-studies) in a \emph{MultiStudy} class. Analysis suites are
integrated in a MultiStudy class by linking the data specification tables
of sub-studies. Sub-study specification table entries are linked by mapping
them to a common entry in the specification table class attribute
of the MultiStudy (Figure \ref{fig:example_multi_study}). This enables derivatives from one
sub-study (e.g. brain extracted T1-weighted anatomical) to be referenced
by workflows of other sub-studies (e.g. anatomically constrained DWI
tractography).
